\section{MPI Implementations}
\label{sec:disc:impl}

With respect to geographical distribution of MPI implementations, several
patterns stand out. In all countries and regions, Open MPI, Intel MPI and MPICH
dominate more than 60\%.

Intel MPI is the most widely used vendor provided MPI implementation all over
the world.  Cray MPI dominates around 10\% in most countries and regions.  From
the less dominant vendors, Fujistu MPI enjoys wider usage than Cray MPI in
Japan, while IBM has visible presence in both Europe and the US.  Although to a
lesser extent, NEC is also in use throughout Europe and Japan.  Finally, there
is only one MPI implementation that stands out with a more international user
base, SGI MPI, although only with a few total mentions all across the world.

On the other end of the spectrum are research oriented implementations, such as
MadMPI with only a few mentions in Europe:France and ParaStation~MPI used
exclusively in Europe:Germany.

Not suprisingly, people who claim higher programming skills (both in general
and with MPI in particular) tend to use a wider range of MPI implementations, a
trend that is most visible in the United States. While most people have no
choice over which implementations they use, a large part of the answers in the
US indicate familiarity with OpenMPI as the primary reason for their choice. On
the other hand, many of the responders in Russia seemed to have no particular
reason when selecting their favorite implementation.

% Russia and Italy satisified with MPI performance (esp. with OpenMPI)? :)


