
ECP Survey\cite{osti_1462877}

\begin{description}
\item Q1:What is your main occupation
\item Q2:Select main country or region of your workplace in past 5 years
\item Q3:Rate your overall programming skill (non-MPI programs)
\item Q4:Rate your MPI programming skill
\item Q5:What programming language(s) do you use most often?
\item Q6:How long have you been writing computer programs (incl. non-MPI programs)?
\item Q7:How long have you been writing MPI programs?
\item Q8;Which fields are you mostly working in?
\item Q9:What is your major role at your place of work?
\item Q10:Have you ever read the MPI standard specification document?
\item Q11:How did you learn MPI?
\item Q12:Which MPI book(s) have you read?
\item Q13:Which MPI implementations do you use?
\item Q14:Why did you choose the MPI implementation(s)?
\item Q15:How do you check MPI specifications when you are writing MPI programs?
\item Q16:What is the most difficult part of writing an MPI program?
\item Q17:Which MPI features have you never heard of?
\item Q18:What aspects of the MPI standard do you use in your program in its current form?
\item Q19:Which MPI thread support are you using?
\item Q20:What are your obstacles to mastering MPI?
\item Q21:When you call an MPI routine, how often do you check the error code of the MPI routine  (excepting MPI-IO)?
\item Q22:In most of your programs, do you pack MPI function calls into their own file or files to have your own abstraction layer for communication?
\item Q23:Have you ever written MPI+”X” programs?
\item Q24:Is there any room for performance tuning in your MPI programs?
\item Q25:What, if any, alternatives are you investigating to indirectly call MPI or another communication layer by using another parallel language/library?
\item Q26:If there were one communication aspect which is not enough in the current MPI could improve the performance of your application, what would you prioritize? Or is MPI providing all the communication semantics required by your application? If not, what is missing?
\item Q27:Is MPI providing all the communication semantics required by your application? If not, what is missing?
\item Q28:What MPI feature(s) are NOT useful for you application?
\item Q29:Do you think the MPI standard should maintain backward compatibility?
\item Q30:In the tradeoff between code portability and performance, which is more or less important for you to write MPI programs?
\end{description}
