\item China: Reading existing code
\item Europe:France: Help from collegues
\item Europe:France: I read MPI softwares written by experienced users
\item Europe:France: I used online resources
\item Europe:France: Stack overflow
\item Europe:France: by example working on a code which was using MPI
\item Europe:France: by programming and my friend "Google"
\item Europe:France: existing code + man pages
\item Europe:Germany: Experimenting. I've been using MPI since 1993
\item Europe:Germany: From experts and interaction with MPI-Forum members
\item Europe:Germany: I looked at code
\item Europe:Germany: I read man pages. I coded.
\item Europe:Germany: Learning by doing
\item Europe:Germany: MPI course at HLRS
\item Europe:Germany: Member of the MPI Forum since MPI-2.0
\item Europe:Germany: Trial \& Error :-)
\item Europe:Germany: colleagues
\item Europe:Germany: course
\item Europe:Germany: courses at various HPC centres
\item Europe:Germany: learning by doing
\item Europe:Germany: learning by doing
\item Europe:Italy: By learning from already written codes
\item Europe:Italy: Collegues
\item Europe:Italy: looking at pre-existing codes
\item Europe:UK: Discussions with peers
\item Europe:UK: Experimented
\item Europe:UK: Learned by doing mostly - worked on codes at the beginning of my PhD and just picked up the basics from there, with more advanced stuff being self taught
\item Europe:UK: Learned from how MPI is used in existing code-base
\item Europe:UK: Learnt by studying other peoples' code
\item Europe:UK: from peers and search engines
\item Europe:UK: trial, error and google
\item Europe:others: By reading existing code
\item Europe:others: I learned from other working applications
\item Europe:others: I read code !
\item Europe:others: I usually look up while working what I need in the html version(s) of the MPI standard documents.
\item Europe:others: I work with MPI quite a lot
\item Europe:others: Like any other programming skill also through some trial-and-error
\item Europe:others: Looking in existing MPI patterns into software application codes
\item Europe:others: Reverse engineering
\item Europe:others: Stackoverflow, Existing Code
\item Europe:others: colleagues
\item Europe:others: going through the source code of MPI-enable applications
\item Europe:others: lecture in High Performance Computing Center (HLRS)
\item Europe:others: manpage
\item Japan: I read existing codes.
\item USA: Biggest learning tool was making toy programs and seeing performance.
\item USA: I read code.
\item USA: I read code.
\item USA: MPI Forum
\item USA: On the job training
\item USA: web
