\item Europe:France: My job is to tune them
\item Europe:France: There is room but it's hardware dependant
\item Europe:France: Yes there remains room but the code will became too complex.
\item Europe:Germany: My programs are usually micro-benchmarks which evaluate performance of MPI.
\item Europe:Germany: Several communication patterns for adapting to implementation of MPI on a specific machine
\item Europe:Germany: There is overhead analysis to be done (tools programming).
\item Europe:Germany: Yes, I know there is room for tuning but re-writing the applications for performance must be balanced with other considerations.
\item Europe:Germany: Yes, based on regular benchmarking other people in my team do the tuning.
\item Europe:Germany: Yes, but first the algorithm has to work!
\item Europe:Germany: Yes, there is room, but the time consuming parts are already optimised
\item Europe:Germany: it depends, I have many projects
\item Europe:Italy: Yes, we plan to tune performance periodically
\item Europe:Italy: yes, to tune programs is my job
\item Europe:UK: I am actively working on it.
\item Europe:UK: I think there is room for tuning, but other developers are looking at it.
\item Europe:UK: Yes but "premature optimisation is the root of all evil" - i.e. it's good enough so better investing time elsewhere
\item Europe:UK: Yes, and am constantly doing so as the code evolves (\verb!>!100 devs)
\item Europe:UK: Yes, but I can not be bothered
\item Europe:UK: Yes, there is room for improvement. Justifying the developer time for the improvement can be challenging if the current performance is "good enough".
\item Europe:UK: Yes, we are doing this.
\item Europe:others: I think the MPI implementation could be tuned, but I had no time to experiment with that so far.
\item Europe:others: I work on MPI performance, but one can always do better.
\item Europe:others: No, the performance-critical layer is primarily OpenMP.
\item Europe:others: The application is latency bound, so even measuring at scale where a problem might exist is so hard it means we tackle other projects
\item Europe:others: There is always room for more tuning
\item Europe:others: Tuning employed when economically viable.
\item Europe:others: Yes and we are working on that
\item Europe:others: Yes, we are working on it.
\item Europe:others: most happens within PETSc, which is a well-tuned MPI library (I think)
\item Japan: Yes, but it's an MPI implementation issue.
\item Russia: My program - is MPI tool.So I do not need MPI performance tuning.
\item South Korea: Application performance varies according to the combination of MPI functions, so it is highly required to select apropriate ones.
\item USA: I believe there should be another option: "MPI does not provide the option that I need for performance tuning."
\item USA: Work on tuning is underway.
\item USA: Yes, I am actively doing tuning work
